Response to reviewers and editorial comments for "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2023-01-17 src/docs_paper/paper.Rmd
Covariates text and refresh online copies

We have the least confidence in our estimates for the FSW risk group.
As well as having the smallest sample sizes, our transactional sex estimates do not overcome the difficulties of sampling hard to reach groups.
We inherent any limitations of the national FSW estimates [@stevens2022estimating] which we adjust our estimates of transactional sex to match.
<!-- (As presented by Oli's paper) -->
Furthermore, we do not consider seasonal migration patterns, which may particularly affect FSW size.
More generally, we did not aim to include predictive covariates.

>>>>

We have the least confidence in our estimates for the FSW risk group.
As well as having the smallest sample sizes, our transactional sex estimates do not overcome the difficulties of sampling hard to reach groups.
We inherent any limitations of the national FSW estimates [@stevens2022estimating] which we adjust our estimates of transactional sex to match.
<!-- (As presented by Oli's paper) -->
Furthermore, we do not consider seasonal migration patterns, which may particularly affect FSW size.
More generally, we did not aim to include predictive covariates.
Many covariates that might be predictive of risk group proportions (for example sociodemographic characteristics, education, local economic activity, cultural and religious norms and attitudes) are themselves difficult to measure spatially, and previous efforts have only led to modest improvements in model performance.
Identifying measurable correlates of risk, or particular settings in which time-concentrated HIV risk occurs, is an important area for further research to improve risk priorisation and precision HIV programme delivery.

### 2023-01-17 src/docs_review/review.Rmd
Covariates text and refresh online copies

> Comment here.

@@

```{r}
df <- read_csv("depends/aaa-variance-proportions.csv")
sobol <- 100 * mean(df$percentage_variance_sur_idx, na.rm = TRUE)
```

We share the reviewer's interest in the spatiotemporal interaction in risk group proportions, which would allow variation in temporal trend by country.
However, we found that these interactions made the model computationally intractable to estimate given the large number of districts, years, age groups and risk groups involved.
This is a limitation of our analysis, but, in practice, we do not believe this has a large impact on our results because overall we found that risk group proportions were very stable over time, while they varied substantially spatially.
More specifically, when we fit the model to each country individually, which can be considered as an extreme version of country-specific spatiotemporal interactions, the proportion of variance (Sobol' index) attributable to the temporal (survey) random effects^[For those countries where such a random effect could be meaningfully defined.] was on average `r sobol`/% (Supplementary Figure B.3).
This is corroborated by the lack of temporal trends in Figures B.5 through B.17 which show the modelled and direct estimates for each country individually, as well as the fact that unstructured (IID) rather than structured (AR1) temporal random effects were preferred in the model selection (Supplementary Figure A.1).

@@

>>>>

> More generally, we did not aim to include predictive covariates. Many covariates that might be predictive of risk group proportions (for example sociodemographic characteristics, education, local economic activity, cultural and religious norms and attitudes) are themselves difficult to measure spatially, and previous efforts have only led to modest improvements in model performance. Identifying measurable correlates of risk, or particular settings in which time-concentrated HIV risk occurs, is an important area for further research to improve risk priorisation and precision HIV programme delivery.

@@

```{r echo=FALSE, results='hide', warning=FALSE, message=FALSE}
df <- read_csv("depends/aaa-variance-proportions.csv")
sobol <- 100 * mean(df$percentage_variance_sur_idx, na.rm = TRUE)
```

We share the reviewer's interest in the spatiotemporal interaction in risk group proportions, which would allow variation in temporal trend by country.
However, we found that these interactions made the model computationally intractable to estimate given the large number of districts, years, age groups and risk groups involved.
This is a limitation of our analysis, but, in practice, we do not believe this has a large impact on our results because overall we found that risk group proportions were very stable over time, while they varied substantially spatially.
More specifically, when we fit the model to each country individually, which can be considered as an extreme version of country-specific spatiotemporal interactions, the proportion of variance (Sobol' index) attributable to the temporal (survey) random effects^[For those countries where such a random effect could be meaningfully defined.] was on average `r sobol`/% (Supplementary Figure B.3).
This is corroborated by the lack of temporal trends in Supplementary Figures B.5 through B.17 which show the modelled and direct estimates for each country individually, as well as the fact that unstructured (IID) rather than structured (AR1) temporal random effects were preferred in the model selection (Supplementary Figure A.1).

@@

Response here.
Requested that coauthors send their COIs.
